---
title: "Data Manipulation - Dplyr"
output:
  pdf_document: default
  html_notebook: default
---

## Importing the libraries
```{r}
library(dplyr)
```

## Importing the data-sets
```{r}
df = read.csv('Allometry.csv')
head(df)
```

## 1) Select the first three columns
```{r}
ans1 <- data.frame(df %>% select(c(1:3)))
head(ans1)
```

## 2) Select all columns except the species column
```{r}
ans2 <- data.frame(df %>% select(-species))
head(ans2)
```

## 3) Select all the rows where both diameter and height are greater than 20
```{r}
ans3 <- (df %>% filter(diameter > 20 & height > 20))
head(ans3)
```

## 4) Arrange the rows by height
```{r}
ans4 = df %>% arrange(height)
head(ans4)
```

## 5) Arrange the rows by Species and then by height
```{r}
ans5 = df %>% arrange(species, height)
head(ans5)
```

## 6) Create a new column by dividing the leafarea with branchmass
```{r}
ans6 = df %>% mutate(leftarea_divide_branchmass = leafarea / branchmass)
head(ans6)
```

## 7) Find the average diameter for each species
```{r}
ans7 = df %>% group_by(species) %>% summarize(avg_diameter = mean(diameter)) 
head(ans7)
```

## 8) Create a new data frame containing 10th to 35th rows of the data
```{r}
ans8 = df %>% slice(10:35)
head(ans8)
```



