# S.PRASHANTH-19MID0020

---
title: "R Notebook"
Date: 10-01-2022
output:
  html_document:
    df_print: paged
---

```{r}
allom <- read.csv("df_Allometry.csv")
head(allom)
```

1.  Create a new column ratio of height

```{r}
allom$ratio = with(allom,height/diameter)
head(allom)
```

2.  Rename column name of 4th Column

```{r}
names(allom)[4] = "lfarea"
head(allom)
```

3.  Select the values \>3 and \<15

```{r}
n1 <- c(1,5,3,86,4,75,24,73,24,15,8,6)
n1[n1>3 & n1<15]
```

4.  Select the rows which have a leaf area \>100 and branchmass\>500

```{r}
allom[allom$lfarea>100 & allom$branchmass>500,]
subset(allom,lfarea>100 & branchmass>500)
```

5.  Read the rain.csv file

```{r}
rain = read.csv("df_rain.csv")
head(rain)
```

6.  Take the subset of data where rain\>20

```{r}
head(rain[rain>20,])
```

7.  What is the mean rainfall for the days where the rain was at least 5

```{r}
mean(rain[rain$Rain>=5,"Rain"])
```

8.  List the day of the year(DOY) where the rain was exactly 0 or 0.7

```{r}
head(rain[rain$Rain==0 | rain$Rain==0.7,c("DOY","Rain")])
```

9.  What is the maximum value of rain

```{r}
rain[which.max(rain$Rain),]
```

10. Display the DOY on which we had maximum rain

```{r}
rain[which.max(rain$Rain),c("DOY","Rain")]
```
