---
title: "R Notebook"
output: html_notebook
---
```{r}
library(ggplot2)
```

```{r}
gender_vector = c("Male", "Female", "Female", "Male", "Male")
cat(class(gender_vector))
```

```{r}
cat(levels(gender_vector))
```

### After factorizing 
```{r}
factor_gender_vector = factor(gender_vector)
cat(class(factor_gender_vector))
```

```{r}
print(levels(factor_gender_vector))
```

```{r}
print(nlevels(factor_gender_vector))
```


## Nominal Categorical variable
A categorical variable has several values but the order does not matter. For instance, male or female. Categorical variables in R does not have ordering.
```{r}
# Create a color vector
color_vector = c('blue', 'red', 'green', 'white', 'black', 'yellow')

# Convert the vector to factor
factor_color = factor(color_vector)
factor_color
```

## Ordinal Categorical variable
Ordinal categorical variables do have a natural ordering. 
We can specify the order, from the lowest to the highest with order = TRUE and highest to lowest with order = FALSE.
```{r}
# Create Ordinal categorical vector 
day_vector = c('evening', 'morning', 'afternoon', 'midday', 'midnight', 'evening')

# Convert `day_vector to a factor with ordered level
factor_day = factor(day_vector, order = TRUE, levels =c('morning', 'midday', 'afternoon', 'evening', 'midnight'))
```


```{r}
summary(factor_day)
```


```{r}
?mtcars
```

```{r}
mtcars$vs
```

```{r}
factor(mtcars$vs)
```


```{r}
ggplot(mtcars, aes(x=vs)) + geom_bar(color='black') 
```
```{r}
ggplot(mtcars, aes(x=factor(vs))) + geom_bar(color='black') 
```

```{r}
?mtcars
```

```{r}
?ToothGrowth
```


```{r}
```


```{r}
colnames(ToothGrowth)
```


```{r}
```


```{r}
```

