---
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---
# Prashanth.S 19MID0020
## Univariate Analysis
### 1) Summary Statistics --> Determines the value’s center and spread.
### 2) Frequency Table    --> Determines how frequently various values occur.
### 3) Charts --> Visual representation of the distribution of values.

## Loading the libraries
```{r}
library(plotly)
library(RColorBrewer)
library(ggplot2)
library(dplyr)
library(plyr)
```

## Diamond Data-Set
```{r}
df1 = diamonds
head(df1)
```

### PreProcessing
```{r}
cat("Number of instances  : ",nrow(df1))
cat("\nNumber of attributes : ",ncol(df1))
```

```{r}
## entire description of the data-set
?diamonds
```


```{r}
str(df1)
```
## Summary Statistics
```{r}
summary(df1)
```
## Frequency Table
```{r}
df_cut = data.frame(table(df1$cut))
df_cut
```

### Bar-Chart
```{r}
table(df1$cut)
```

```{r}
## Normal Count of the cut
ggplot(df1, 
       aes(x=factor(cut),fill = factor(cut))) +
       geom_bar(color='black') + 
       labs(x = "Cut", y = "Count", title  = "Count of the quality of the Cut")
```

```{r}
count(df1$cut)
```

```{r}
## Percentage of the Count of the cut
ggplot(df1, 
       aes(x = cut, y = ..count.. / sum(..count..),fill = factor(cut))) + 
       geom_bar(color='black') +
       labs(x = "Cut", y = "Percentage of Cuts", title  = "Percentage of the quality of the Cut") +
       scale_y_continuous(labels = scales::percent)
```

### Pie-Chart
```{r}

```

### Kernel Density Plot
```{r}
ggplot(df1, aes(x = price)) +
       geom_density(fill = "indianred3") + 
       labs(title = "Participants by price")
```

## MPG data-set
```{r}
df2 = mpg
head(df2)
```
### PreProcessing

```{r}
cat("Number of instances  : ",nrow(df2))
cat("\nNumber of attributes : ",ncol(df2))
```

```{r}
str(df2)
```

```{r}
summary(df2)
```

```{r}
df2 %>%
    summarize(variable = "cty",
              q0.2 = quantile(cty, 0.2), ## 20% city values
              q0.4 = quantile(cty, 0.4), ## 40% cty values
              q0.6 = quantile(cty, 0.6), ## 60% cty values
              q0.8 = quantile(cty, 0.8)) ## 80% cty values
```

```{r}
df2 %>%
    summarize(
      variable = "cty", 
      mean = mean(cty), 
      variance = var(cty),
      standard_deviation = sd(cty),
      Inter_Quartile_Range = IQR(cty)
)
```

```{r}
df2 %>%
    group_by(drv) %>%
    summarize(mean_cty = mean(cty), Standard_Deviation_cty = sd(cty))
```

### Barchart
```{r}
ggplot(df2, 
       aes(x = factor(cyl), y = ..count.. / sum(..count..),fill = factor(cyl))) + 
       geom_bar(color='black') + 
       labs(x = "Cylinders", y = "Percentage of Cylinders", title  = "Role of Number of Cylinders") +
       scale_y_continuous(labels = scales::percent)
```

```{r}
ggplot(df2, aes(factor(manufacturer),fill = factor(manufacturer))) +
      geom_bar(color='black') +
      labs(x = "Count", y = "Manufactures", title  = "Participation of Manufactures") + 
      coord_flip()
```

### Kernel Density Plot
```{r}
ggplot(df2, aes(x = year)) +
       geom_density(fill = "indianred3") + 
       labs(title = "Participants by Year")
```

### bivariate analysis
```{r}
df2 %>%
    ggplot(aes(cty)) +
    geom_histogram(binwidth = 1.25, color = "black",fill = "grey") +
    labs(
        title = "Distribution of cty",
         x = "city",
         y = "Number of cars"
    ) 
```

```{r}
df2 %>%
    ggplot(aes(drv,cty)) +
    geom_boxplot() +
    labs(title = "Distribution of cty relative to Driving Mode",
         x = "Driving Mode",
         y = "cty-value")
```




