---
title: "Plotly Plots"
output: html_notebook
---

```{r}
library(plotly)
library(RColorBrewer)
library(ggplot2)
```

```{r}
head(iris)
```


```{r}
plot_ly(data=iris, x=~Sepal.Length, y=~Petal.Length, mode='markers')
```


```{r}
## rgba --> red, green, blue, alpha
plot_ly(data=iris, x=~Sepal.Length, y=~Petal.Length, mode='markers', 
        marker=list(size=10, color='rgba(255,170,190,.9)'))
```


```{r}
plot_ly(data=iris, x=~Sepal.Length, y=~Petal.Length, mode='markers', 
        marker=list(
            size=10, color='rgba(255,100,100,.9)',
            line = list(color='rgba(200,0,0,0.9)',width=2)
            )
        )
```

```{r}
---
title: "Plotly Plots"
output: html_notebook
---

```{r}
library(plotly)
```

```{r}
head(iris)
```


```{r}
plot_ly(data=iris, x=~Sepal.Length, y=~Petal.Length, mode='markers')
```


```{r}
## rgba --> red, green, blue, alpha
plot_ly(data=iris, x=~Sepal.Length, y=~Petal.Length, mode='markers', 
        marker=list(size=10, color='rgba(255,170,190,.9)'))
```


```{r}
plot_ly(data=iris, x=~Sepal.Length, y=~Petal.Length, mode='markers', color = ~Species)
```

```{r}
par(mar=c(3,4,1,1))
display.brewer.all(
)
```
```{r}
plot_ly(data=iris, x=~Sepal.Length, y=~Petal.Length, mode='markers', color=~Species, colors='Set1')
```

```{r}
col = c("red", "blue", "green")
plot_ly(data=iris, x=~Sepal.Length, y=~Petal.Length, mode='markers', color=~Species, colors=col)
```

```{r}
## Now virginica->red, setosa->blue, versicolor->green
col = c("red", "blue", "green")
col = setNames(col, c("virginica", "setosa", "versicolor"))
plot_ly(data=iris, x=~Sepal.Length, y=~Petal.Length, mode='markers', color=~Species, colors=col)
```

```{r}
## Now virginica->red, setosa->blue, versicolor->green
col = c("red", "blue", "green")
col = setNames(col, c("virginica", "setosa", "versicolor"))
plot_ly(
        data=iris, x=~Sepal.Length, y=~Petal.Length, mode='markers', 
        color=~Species, colors=col, 
        symbol=~Species, symbols=c('circle', 'x', 'pentagon')
      )
```

```{r}
col = c("red", "blue", "green")
col = setNames(col, c("virginica", "setosa", "versicolor"))
plot_ly(
        data=iris, x=~Sepal.Length, y=~Petal.Length, mode='markers', marker=list(size=10),
        text=~paste("Sepal-Width : ",Sepal.Width,"Petal-Width : ",Petal.Width),
        color=~Species, colors=col, 
        symbol=~Species, symbols=c('circle', 'x', 'pentagon')
      )
```

## Line Plot
```{r}
day = c(1:30)
num = rnorm(n=30, mean=3)
df = data.frame(day, num)

head(df)
```

```{r}
plot_ly(df, x=~day, y=~num, type='scatter')
```

```{r}
plot_ly(df, x=~day, y=~num, type='scatter', mode='lines')
```


```{r}
plot_ly(df, x=~day, y=~num, type='scatter', mode='lines+markers', line=list(color='red', width=2))
```


```{r}
```

## ggplot to plotly plot
```{r}
p = ggplot(iris, aes(x=Sepal.Length, y=Petal.Length)) + geom_point() ## ggplot
ggplotly(p) ## plotly plot
```

## Bar-Graph
```{r}
fruits = c("apple", "banana", "orange")
count_c = c(200,150,300)
count_b = c(100,250,150)

df1 = data.frame(fruits, count_c, count_b)
head(df1)
```

```{r}
plot_ly(df1, x=~fruits, y=~count_c, type='bar')
```
### using add_trace
```{r}
p = plot_ly(df1, x=~fruits, y=~count_c, type='bar', name='location-1')
p%>%add_trace(y=count_b, name='location-2')
```

